The Spine of American Legal Practice

### 2016-06-27 article/article.Rmd
Network graph and caption for the table

@@

Comparing the section pairs above produces the following matrix of scores.

@@

@@

Having developed a method for finding legislative borrowings, we next sought to visualize the broader patterns revealed by the those borrowings. We did this first by aggregating the section to section borrowings into code to code borrowings. By counting how many sections each code borrowed from each other code, we were able to show the connections from one code to another.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(igraph)
library(ggplot2)
library(ggraph)
load("../cache/network-graphs.rda")
source("../R/helper.R")
set.seed(82893)
```

@@

Comparing the section pairs above produces the matrix of similarity scores in table 1.

@@

  Table: A subset of the section to section similarity matrix.

@@

Having developed a method for finding legislative borrowings, we next sought to visualize the broader patterns revealed by those borrowings. We did this first by aggregating the section to section borrowings into code to code borrowings. By counting how many sections each code borrowed from each other code, we were able to show the connections from one code to another.

```{r code-to-code-network, fig.width=12, fig.height=12, fig.cap = "The structure of borrowings among nineteenth-century codes of civil procedure. Note that several versions of New York's Field Code were at the center of the network, while other states such as California and Ohio became centers of regional variations on the Field Code."}
ggraph(codes_g, "igraph", algorithm = "nicely") +
  geom_edge_fan(aes(edge_width = sections_borrowed, 
                    alpha = sections_borrowed),
                arrow = arrow(type = "closed", ends = "first",
                              length = unit(0.20, "inches"),
                              angle = 15)) +
  geom_node_point(aes(colour = as.factor(distance)), size = 10) +
  scale_edge_width("Sections borrowed", range = c(1, 2), guide = "none") + 
  scale_edge_alpha(range = c(0.3, 0.6), guide = "none") +
  scale_color_discrete("Distance from a NY code") +
  ggforce::theme_no_axes() +
  geom_node_text(aes(label = name), size = 6) +
  # labs(title = "Borrowings among nineteenth-century codes of civil procedure") +
  theme(legend.position = "bottom",
        panel.border = element_blank())
```
